\documentclass[twocolumn]{article}
%\usepackage{natbib}
\usepackage{graphicx}
%\usepackage[margin=0.800in]{geometry}
\usepackage{setspace}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{color}
\usepackage{parskip}
%\usepackage[small,compact]{titlesec}
\usepackage[format=hang]{caption}
%\usepackage{float}
\usepackage{titling}

\title{N-gram Based Grammar Correction}
%\date{\today}
\date{}

\newcommand{\tab}{\hspace*{2em}}


\begin{document}
%\bibliographystyle{alpha}
%\bibliographystyle{apalike}
\bibliographystyle{acm}

\maketitle
\section{Problem Statement}
Spelling and grammar errors infest the lives of everyone from native to
non-native speakers of a language. We will consider the problem of spelling and
grammar correction. Traditionally, spell checking utilizes a dictionary, but
this creates the problems of out-of-vocabulary and data sparseness. To overcome
this many have used a corpus, a database of existing texts, usually hundreds of
books and newspapers. These corpora can be tagged or untagged. A tagged corpus
contains, for each word, a tag describing which part of speech the word
represents. The corpus is usually preprocessed into counts of n-grams. An n-gram
is a sequence of tokens, usually words or characters of length n. Usually,
n-grams are extracted from a corpus by taking all possible substrings of tokens
or words of length n of all sentences in the corpus. Different approaches to
solving the problem include using tagged or untagged corpora and using n-grams
with different n in different parts of the error correction process.

In a related field, machine translation does not traditionally utilize much
language data (except for the translation model), which \cite{norvig09}
suggested could improve translation. This suggests a naive improvement for
machine translation: run a spell checker on poorly translated text.

We have considered using an untagged corpus and counts of combinations of
different sized word punctuation n-grams to check for spelling and grammar
mistakes in texts and translations, and offer corrections based on these counts.

\section{Related Work}
Traditional techniques include using a language model including a grammar model
of the language. Relatively recently (\cite{michel11} published one of the first
datasets in 2006) other techniques using probabilistic models of language with
much bigger datasets have started taking over and offered much better accuracy.

The technique described by \cite{Fossati07} uses 3-grams consisting of words and
parts-of-speech and checks for errors based on their probability of occurrence
in a tagged corpus. This method is insufficient because it does not vary the
size of the n-grams. It also incorporates part-of-speech, which increases
permutations and complexity.

The algorithm by \cite{Bassil12} is comprised of a spelling error checker using
unigrams information from Yahoo! N-Grams Dataset; a candidates generator based
on a letter-based 2-gram model; and a context-sensitive error corrector that
selects the best spelling candidate for correction using 5-grams information
from Yahoo! N-Grams Dataset.

\section{Implementation Details}
Our implementation is based on known approaches utilizing three phases:

We implemented a spelling and grammar checker using a corpus of n-grams. We transformed the 1-million word Brown corpus from the Natural Language Toolkit into n-grams by extracting substrings of tokens of length \textit{n} equal to 1 through and scored them based on frequency in the corpus. Tokens are either words, punctuation symbols or start- or end-of-sentence symbols.

First, trigrams were used for correction. For this, we extracted all trigrams in
 each sentence and found a confusion set of words that each middle word in the
trigram could be confused with. To do this we searched the corpus of scored
trigrams using a merge algorithm to find all trigrams that were identical to
those of the trigram in the sentence being corrected except for the middle word.
Here is an example of confusion set search for the trigram
\\
\newline
\tab\tab\textit{He went home}
\\\newline
Merged trigrams in the corpus would be of the form:
\\\newline
\tab\tab\textit{He ran home} \\
\tab\tab\textit{He was home} \\
\tab\tab\textit{He walked home}
\newline

So the confusion set would be: \{\textit{ran, was, walked}\}. Candidate sentences
were then generated using the confusion set for each word in a sentence. Next,
the Damerau-Levenshtein distance \cite{damerau64,levenshtein66} algorithm (an 
algorithm that calculates the edit distance between two words, that is the number 
of insertions, substitutions, deletions and transpositions needed to change one 
word into another) was used to determine how similar each word in each candidate sentence was to the
corresponding word in the original text. The three candidate sentences with the
least distance and highest score are returned. These candidate words are then
combined into candidate sentences.

The second phase is to score each candidate sentence by creating uni-, bi-,
tri-, 4- and 5-grams from the candidate sentences and then score those scored
trigrams based on the n-grams from the corpus.

The final phase is to put these scores together and select the best candidate.
For each sentence we summed each set of n-grams to generate a total score for
each type of n-gram. This was done for each original sentence and its candidate
sentences. We used the same technique to calculate the total edit distance to
the original sentence and used that as a score too. A linear interpolation of
these scores using manually adjusted weighting produced final evaluation values
used to select the correct sentence. After performing this evaluation and
selection for all the sentences in the documents, The corrected document was
compared to the original document using word error rate (WER) which is similar to the Damerau-Levenshtein distance algorithm, except uses a faster version using the Levenshtein distance.

\section{Evaluation}
For evaluation, we used two methods. The first method evaluated our improvement
of a poor translation. We constructed the poor translation by taking a document
manually translated to traditional Chinese and using Google translate,
translated this document to English. We then compared this text using WER (Word
error rate) to the original English version of the document to get a base score.
To evaluate our algorithm we ran this poorly translated text through our
algorithm and compared the results with the original document using WER, which
is the percent difference between the documents. We did this using two different
methods of finding errors, using just trigrams, and using n-grams with \textit{n} equal
to 1 through 5. We put this translated document into Microsoft Word, corrected
errors if suggestions were given and compared this to the original document
using WER. The results are shown in Table~\ref{gpl}.

\begin{table}[h]
\centering
\begin{tabular}{ | c | c | c | }
\hline
Evaluation & Technique & Percent \\
Technique & Used & Different \\
\hline
Distance & Original & 61\% \\
\cline{2-3} Algorithm & 3-grams & 68\% \\
\hline
Word & Original & 61\% \\
\cline{2-3} Error Rate & 1-5 grams & 61\% \\
\cline{2-3} (WER) & MS Word & 66\% \\
\hline
\end{tabular}
\caption{Evaluation of original English text vs. translated text and corrected translation using different evaluation techniques and correction methods.}
\label{gpl}
\end{table}

The second method we used to evaluate our approach was trying to correct errors
introduced into a text. We did this by choosing \textit{n} sentences randomly in a
test text and then introducing one error per sentence. We then ran those
sentences through our algorithm and counted the number of correctly corrected
sentences and uncorrected or falsely corrected sentences. Our average percentage
of correct sentences was 72\%, with 28\% divided between errors not corrected
and falsely-corrected words. \cite{Bassil12} used this same approach to test
their algorithm and came up with impressive results due to their use of a
3.4-billion word corpus tagged with parts-of-speech, whereas \cite{Fossati07}
used a corpus of 1-million words. The results of \cite{Bassil12} and
\cite{Fossati07} are shown in table~\ref{text}

\begin{table}[h]
    \centering
    \begin{tabular}{ | l | c | c | c | }
        \hline
        Types of & Well & Not & Falsely \\
        Corrections & Corrected & Corrected & Corrected \\
        \hline
        Ours & 0.72 & 0.16 & 0.16 \\
        \hline
        Bassil\cite{Bassil12} & 0.94 & 0.2 & 0.4 \\
        \hline
        Fossati\cite{Fossati07} & 0.50 & 0.32 & 0.14 \\
        \hline
    \end{tabular}
    \caption{Results of correcting errors introduced into a text}.
    \label{text}
\end{table}

\section{Discussion}
A larger corpus would definitely have helped, given a powerful enough computer
to handle it. The use of a small corpus tends to produce worse results because
of data sparseness, which gives rise to situations where the correction does not
exist in the corpus, making such corrections impossible without a grammar model.
In the first test, we learned that word error rate is a faster and better 
algorithm in our situation for determining the distance between n-grams, as the
shown in table~\ref{gpl}.
The results in table~\ref{text} show that software such as Microsoft Word and
almost all other do a very poor job at performing grammar correction.
Something to conclude from our testing is that software such as Google Translate
and Bing Translate probably already utilizes the same information found in a
corpus to do this sort of check during their translations, and therefore our
effort becomes redundant and ineffective.
By training the weighting of the scores for each type of n-gram our algorithm
could have produced improved results.
\cite{Bassil12} generated a confusion set by using bigrams of characters and
evaluating those. We used a different approach, that while being more complete,
was also slower. The slowest part of our algorithm was actually choosing the
confusion set for each character by measuring the edit-distance between the
original word and the candidate. Using the faster Levenshtein distance instead
of the Damerau-Levenshtein distance we achieved a considerable speedup. Overall
we learned that using solely n-grams to correct grammar is insufficient, and the
use of some property of grammar is necessary, whether it be a part-of-speech
tagging or some other method. If we were to change something it would be to use
a grammar model. The effect of using an extremely large corpus could be
investigated as well, but a grammar model would most likely be more accurate.
Also, especially in the area of foreign language translation, semantic modeling
would be interesting to investigate.

%\begin{spacing}{0.9}
\small
\bibliography{References}
%\end{spacing}
\end{document}
